### 2018-07-04 cv-body.tex
Fix cv
Update

\section{Professional experience}\label{professional-experience}

@@

\section{Education}\label{education}

@@

\section{Publications}\label{publications}

@@

@@

\section{Awards and scholarships}\label{awards-and-scholarships}

\begin{description}
\tightlist
\item[2017]
Canadian Society for Ecology and Evolution (CSEE) Early Career Award
(\href{http://csee-scee.ca/?p=5183}{URL})
\item[2015]
David H. Smith Conservation Postdoctoral Research Fellowship
(\href{http://conbio.org/mini-sites/smith-fellows/meet-the-fellows/2015-fellows/sean-anderson}{URL})
\item[2015]
Simon Fraser University Dean of Graduate Studies Convocation Medal
(\href{https://www.sfu.ca/dean-gradstudies/blog/year/2015/06/SeanAnderson.html}{URL})
\item[2014]
Garfield Weston Foundation / BC Packers Ltd. Graduate Fellowship in
Marine Sciences
\item[2014]
Graduate Fellowship (two semesters), Simon Fraser University
\item[2012--13]
Canadian Fulbright Scholar award to the University of Washington
\item[2011]
Canadian \href{http://goo.gl/nA1zE}{Governor General's Academic Gold
Medal} for the top-ranked Master's Natural Sciences and Engineering
thesis at Dalhousie University in 2010
\item[2011--14]
Provost Prize of Distinction, Simon Fraser University
\item[2011--14]
Natural Sciences and Engineering Research Council of Canada Postgraduate
Scholarship (Doctoral)
\item[2007--10]
Faculty Research Grant Scholarship, Dalhousie University
\item[2007--09]
Graduate Studies Scholarship, Dalhousie University
\item[2007]
Environmental Programmes Honour Society Medal, Dalhousie University
\end{description}

\section{Software}\label{software}

@@

\section{Invited talks and conference
presentations}\label{invited-talks-and-conference-presentations}

@@

\section{Teaching}\label{teaching}

@@

\section{Contract employment}\label{contract-employment}

@@

\section{Working groups and
workshops}\label{working-groups-and-workshops}

@@

\section{Selected courses and
training}\label{selected-courses-and-training}

@@

\section{Reviews}\label{reviews}

>>>>

\hypertarget{professional-experience}{%
\section{Professional experience}\label{professional-experience}}

@@

\hypertarget{education}{%
\section{Education}\label{education}}

@@

\hypertarget{publications}{%
\section{Publications}\label{publications}}

@@

\textbf{Anderson, S.C.}, T.A. Branch, A.B. Cooper, N.K. Dulvy. Reply to
Youngflesh and Lynch: Migration and population growth rate in animal
black-swan events. Proceedings of the National Academy of Sciences. In
press at Proceedings of the National Academy of Sciences.
\url{https://doi.org/10.1073/pnas.1714157114}
Ward, E.J., \textbf{S.C. Anderson}, A.O. Shelton, R.E. Brenner,
M.D.\ Adkison, A.H. Beaudreau, J.T. Watson, J.C. Shriver, A.C. Haynie,
B.C. Williams. Effects of increased specialization on revenue of Alaskan
salmon fishers over four decades. In press at Journal of Applied
Ecology.

@@

\hypertarget{awards-and-scholarships}{%
\section{Awards and scholarships}\label{awards-and-scholarships}}

\begin{description}
\tightlist
\item[2017]
Canadian Society for Ecology and Evolution (CSEE) Early Career Award
(\href{http://csee-scee.ca/?p=5183}{URL})
\item[2015]
David H. Smith Conservation Postdoctoral Research Fellowship
(\href{http://conbio.org/mini-sites/smith-fellows/meet-the-fellows/2015-fellows/sean-anderson}{URL})
\item[2015]
Simon Fraser University Dean of Graduate Studies Convocation Medal
(\href{https://www.sfu.ca/dean-gradstudies/blog/year/2015/06/SeanAnderson.html}{URL})
\item[2014]
Garfield Weston Foundation / BC Packers Ltd.\ Graduate Fellowship in
Marine Sciences
\item[2014]
Graduate Fellowship (two semesters), Simon Fraser University
\item[2012--13]
Canadian Fulbright Scholar award to the University of Washington
\item[2011]
Canadian \href{http://goo.gl/nA1zE}{Governor General's Academic Gold
Medal} for the top-ranked Master's Natural Sciences and Engineering
thesis at Dalhousie University in 2010
\item[2011--14]
Provost Prize of Distinction, Simon Fraser University
\item[2011--14]
Natural Sciences and Engineering Research Council of Canada Postgraduate
Scholarship (Doctoral)
\item[2007--10]
Faculty Research Grant Scholarship, Dalhousie University
\item[2007--09]
Graduate Studies Scholarship, Dalhousie University
\item[2007]
Environmental Programmes Honour Society Medal, Dalhousie University
\end{description}

\hypertarget{software}{%
\section{Software}\label{software}}

@@

\hypertarget{invited-talks-and-conference-presentations}{%
\section{Invited talks and conference
presentations}\label{invited-talks-and-conference-presentations}}

@@

\hypertarget{teaching}{%
\section{Teaching}\label{teaching}}

@@

\hypertarget{contract-employment}{%
\section{Contract employment}\label{contract-employment}}

@@

\hypertarget{working-groups-and-workshops}{%
\section{Working groups and
workshops}\label{working-groups-and-workshops}}

@@

\hypertarget{selected-courses-and-training}{%
\section{Selected courses and
training}\label{selected-courses-and-training}}

@@

\hypertarget{reviews}{%
\section{Reviews}\label{reviews}}
